\plaintitle

### 2016-09-21 drafts/labor/decomposition.tex
decomposition revised

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

\subsubsection[the decomposition of work]{The Decomposition of Work}\label{sec:decomposition}

\subsubsubsection{\crowdworkpers}
\topic{The crowdsourcing research into work decomposition
has largely focused on minimizing the additional context necessary to do tasks%
, and making it easier to do tasks with less time.}
This first thread is
perhaps best described by \citeauthor{verroios2014context} as
making crowd workers ``\dots able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
With the exception of a few cases
(specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
which finds that greater work context fosters more reliably high--quality work)%
, the micro task paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016%
,       cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes%
, the marginal cost of finding and
\textit{doing} tasks has increasingly become the focus of research.}
\citeauthor{taskSearch} illustrate the challenges on AMT%
, and some work has gone into ameliorating the problems specific to this work site
(\textit{ReLauncher}), % does anyone care for project names?
while other work designs tasks around gap time
(\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning})
\cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996%
,       Cai:2015:WLW:2702123.2702267}.
% \topic{One of the emergent properties of micro--tasks has been the relative cost of
%     \textit{finding} worthwhile tasks.}
%     The research community has documented and to some extent attempted to intervene in
%     the discovery of worthwhile tasks
%     \cite{taskSearch}.
\citeauthor{Cosley:2007:SUI:1216295.1216309}
attempts to address this by
directing workers to tasks through
``intelligent task routing''
\cite{Cosley:2007:SUI:1216295.1216309}.
Much of this work and the work at the periphery of this space, then%
, has focused on
minimizing the amount of time that people need to spend doing
anything other than the work for which they are paid.

Yet more work looks at the general framing of tasks%
, chaining and arranging them to maximally exploit
the attention and stress threshold % ???
of workers
\cite{Cai:2016:CRI:2858036.2858237}.
Rather than attempt to minimize the error rates in micro--tasks%
, as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested%
, we as a community have leaned \textit{into} the peril of
low--context work%
, ``embracing error'' in crowdsourcing
\cite{embracingErrorKrishna}.

\subsubsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{17} century%
, when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute, by hand, astronomical phenomena
\cite{grier2013computers}.
These workers became the first \textit{computers}.

The work Airy solicited was interesting for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values%
, and have other workers check their work.
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

The insight of breaking tasks down into smaller components didn't find its audience until
the early \nth{20} century%
, with the rise of Fordism and scientific management (or Taylorism).
From scientific management, we found that
we could measure work at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out%
, piecework most greatly benefits the instrumented measurement of workers, but certainly
in Ford and Taylor's time --- and certainly in Airy's time ---
highly instrumented, automatic measurement of workers was all but impossible.
As a result%
, the distillation of work into smaller chunks
ultimately reached a limit of usefulness.

\subsubsubsection{\whatchanged}
 \topic{A number of factors in crowdwork are different from piecework,
 chief among them being the relative ease with which
 the metaphorical ``assembly line'' can be changed.}
 Computers make it possible to switch from one task to another
unlike any arbitrary manufacturing factory possibly could;
a worker could do any number of
different \textit{types} of tasks in the span of just a few minutes
\cite{delayAndOrderLasecki}.
This has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to measure consistently as few as 20 years ago
\cite{cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

Further, we've sliced work to such small scales that the marginal activities
--- things like finding work, cognitive task switching, etc\dots ---
have become relatively large compared to the tasks themselves
\cite{taskSearch}.
In the historical case of piecework,
moving metallurgical tools, mining equipment, or
other industry materials would have been prohibitively difficult and slow;
workers were encouraged to specialize in a single set of tasks,
allowing pieceworkers to sequence their tasks optimally on their own
\cite{hart2013rise}.

Rather than fall into the trap that \citeauthor{irani2015cultural} warns of,
--- one which where crowdworkers are rendered as
``modular, protocol--defined computational services'' ---
we may yield better results from crowdwork if we think of workers as similar to
specialized, repurposable tools
\cite{irani2015cultural}.
\ali{feeling meh about this argument\dots}

Finally, instrumentation has reached a sufficiently advanced and ubiquitous point that
the dream of scientific management and Taylorism
--- to measure every motion at every point throughout the workday and beyond ---
is not only doable, but trivial
\cite{waltz2012quantified}.
One of the major challenges \citeauthor{10.2307/23702539} cites as
preventing scientific management from being fully utilized,
the difficulty of tracking work \& workers, no longer exists
\cite{10.2307/23702539}.

\subsubsubsection{\implication}
Crowdwork research today is on the right track to investigate pipelining and meta--task design.
That is, investigating better work discovery methods, producing tools for workers to make more informed decisions
\cite[see, for example,][]{turkopticon}.
It's not clear how much benefit there is in the further decomposition of work,
given that we've hit bottlenecks with the cognitive stresses of switching between tasks
as \citeauthor{delayAndOrderLasecki} highlight
\cite{delayAndOrderLasecki}.

\onlyinsubfile{
  \balance{}
  \printbibliography

  % \clearpage
  % \nobalance{}
  }
%   \endnotetext{
% %     \section{Slicing notes}
% %     The finding here is that
% %     crowdwork can be more carefully micro--managed than piecework could be%
% % ,     and that this is a double--edged sword:
% %     we can effectively give feedback to workers on everything they do%
% % ,     but this is emboldening us to try to
% %     over--manage workers just as piecework tried to do.

% %     My goal for this section is to make two points:
% %     \begin{enumerate}
% %       \item show how this is related to the assembly line and scientific management%
% % ,             and how piecework literature tried to measure everything%
% % ,             but found it untenable given the extra equipment that was necessary
% %             (but generally which didn't exist)
% %             to track every movement and action that workers took.
% %       \item show how this work was enabled by the ``verifiability'' of work output(?)
% %     \end{enumerate}

%     % \ali{i don't like this section \textit{here}, but i like it in general. what do?}

%   }

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\onlyinsubfile{
  \usepackage{xr-hyper}
  \usepackage{hyperref}
}

\begin{document}

\subsection[How far can work be decomposed into smaller microtasks]{Decomposing Work}\label{sec:decomposition}

At its core, on--demand work has been enabled by decomposition of large goals into many small tasks. As such, one of the central questions in the literature is how to design these microtasks, and which kinds of tasks are amenable to decomposition. In this section, we place these questions in the context of piecework's Tayloristic evolution.

\begin{comment}
Outline:
Crowd work
	- How do we take work and split it up into smaller work?
	- How small can we go?
	- Once we split up, what happens? Marketplace choosing
Piecework
	- How do we take work and split it up?
	[ - how small can we go? ]
	[- Nothing about how people choose. ]
Same/different
	[- task data science ]
	[- Cognitive barriers, task switching, etc, dominates]
	[ - Switching is different, marketplace model ]
\end{comment}

\subsubsection{\crowdworkpers}
\topic{Many contributions to the design and engineering of crowd work consist of creative methods for decomposing goals.} Even when tasks such as writing and editing cannot be reliably performed by individual workers, researchers demonstrated that decompositions of these tasks into workflows can succeed~\cite{crowdForgeKittur,bernsteinSoylent,writingMicroTasks,Nebeling:2016:WCW:2858036.2858169}. 
These decompositions typically take the form of workflows, which are algorithmic sequences of tasks that manage interdependencies~\cite{Bigham2014}. 
Workflows often utilize a first sequence of tasks to identify an area of focus (e.g., a paragraph topic~\cite{crowdForgeKittur}, an error~\cite{bernsteinSoylent}, or a concept~\cite{Yu2016a,Yu2016b} and a second sequence of tasks to execute work on that area. 
This decomposition style has been successfully applied across many areas, including food labeling~\cite{noronha2011platemate}, brainstorming~\cite{siangliulue2015toward,yu2014distributed}, and accessibility~\cite{lasecki2013chorus,lasecki2012real,Lasecki2011}.

\topic{If decomposition is key to success in crowd work, the question arises: what can, and can't, be decomposed?} 
Moreover, how thinly can work be sliced and subdivided into smaller and smaller tasks? 
The general trend has been that smaller is better, and the microtask paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
This work illustrates a broader sentiment in both the study and practice
of crowd work, that microtasks should be designed resiliently against the variability of workers, preventing a single errant submission from impacting the agenda of the work as a whole %, fully exploiting the abstracted nature of each piece of work
~\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
In this sense, finer decompositions are seen as more robust --- both to interruptions and errors~\cite{cheng2015break} --- even if they incur a fixed time cost.
At the extreme, recent work has attempted demonstrated microtasks that take seconds~\cite{Vaish:2014:TCC:2611222.2556996,Cai:2015:WLW:2702123.2702267} or even tenths of a second~\cite{embracingErrorKrishna}.
%Earlier we discussed \citeauthor{cheng2015break}'s work measuring the impact that interruption has on worker performance \cite{cheng2015break}.%While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components in the form of higher cumulative time to complete (albeit much shorter real time to complete, owing to parallelization)%
However, workers perform better when similar tasks are strung together 
\cite{delayAndOrderLasecki}, or chained and arranged to maximize  the attention threshold of workers~\cite{Cai:2016:CRI:2858036.2858237}.
Despite this, 
%rather than attempt to minimize the error rates in micro--tasks
%, as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested%
we as a community have leaned \textit{into} the peril of
low--context work, ``embracing error'' in crowdsourcing~\cite{embracingErrorKrishna}.

\topic{The general lesson has been that the more micro the task, and the more fine the decomposition, the greater the risk that workers lose context necessary to perform the work well.}
For example, workers edit adjacent paragraphs in inconsistent ways~\cite{bernsteinSoylent,Kim2017}, interpret tasks in different ways~\cite{kairam2016parting}, and exhibit lower motivation~\cite{Kinnaird:2012:WTM:2389176.2389219} without sufficient context.
Research has sought to ameliorate this issue by designing workflows help workers ``act with global understanding when each contributor only has access to local views''~\cite{verroios2014context}, typically by automatically or manually generating higher-level representations for the workers to reflect on~\cite{chilton2013cascade,verroios2014context,Kim2017}.

% \topic{The crowdsourcing research into work decomposition
% has largely focused on minimizing the additional context necessary to do tasks%
% , and making it easier to do tasks with less time.}
% This first thread is
% perhaps best described by \citeauthor{verroios2014context} as
% making crowd workers ``\dots able to act with
% global understanding when each contributor only has access to local views''
% \cite{verroios2014context}.
% With the exception of a few cases
% (specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
% which finds that greater work context fosters more reliably high--quality work)%
% , the micro task paradigm has emerged as the overwhelming favorite
% \cite{selfsourcingTeevan2014,selfsourcingTeevan2016%
% ,       cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes, the invisible labor of \textit{finding} tasks~\cite{martin2014being} has arisen as a major issue.}
\citeauthor{taskSearch} illustrate the task search challenges on AMT.%
Workers seek out good requesters~\cite{martin2014being} and then  ``streak'' to perform many tasks of that same type~\cite{taskSearch}.
%, and some work has gone into ameliorating the problems specific to this work site (\textit{ReLauncher}), % does anyone care for project names?
%while other work designs tasks around gap time (\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning}) \cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996,       Cai:2015:WLW:2702123.2702267}.
% \topic{One of the emergent properties of micro--tasks has been the relative cost of
%     \textit{finding} worthwhile tasks.}
%     The research community has documented and to some extent attempted to intervene in
%     the discovery of worthwhile tasks
%     \cite{taskSearch}.
Researchers have reacted by designing task recommendation systems (e.g.,~\cite{Cosley:2007:SUI:1216295.1216309})
%attempts to address this by directing workers to tasks through ``intelligent task routing'' \cite{Cosley:2007:SUI:1216295.1216309}.
and others focused on minimizing the amount of time that people need to spend doing anything other than the work for which they are paid~\cite{callison2014crowd}.

\subsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{17} century%
, when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute astronomical phenomena
\cite{grier2013computers}.
%These workers became the first \textit{computers}.

The work that Airy solicited resonates with modern crowd work for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values%
, and have other workers check their work.
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

This approach found its audience in the early \nth{20} century with the rise of Fordism and scientific management (or Taylorism).
Scientific management suggested that it was possible to measure work  at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out, piecework most greatly benefits the instrumented measurement of workers, but certainly in Ford and Taylor's time, highly instrumented, automatic measurement of workers was all but impossible~\cite{Brown01041990}.
As a result, the distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.
\msb{This subsection is too shallow and needs a bit more. For example, can you give examples of the last point?}

\subsubsection{\whatchanged}
\begin{comment}
outline
	- measurement is more precise, so decomposition is deeper
	- not a single position, but a marketplace
\end{comment}

\topic{Where measurement and instrumentation were limiting factors for historical piecework, computation has changed the situation so that a dream of scientific management and Taylorism
--- to measure every motion at every point throughout the workday and beyond ---
is not only doable, but trivial
\cite{waltz2012quantified}.}
Where \citeauthor{10.2307/23702539} directly implicates measurement as
% cites as
preventing scientific management from being fully utilized,
%the difficulty of tracking work \& workers, no longer exists
%\cite{10.2307/23702539}.}
modern crowd work is measuring and modeling every click, scroll, and keyboard event~\cite{rzeszotarski2011instrumenting,rzeszotarski2012crowdscape}.
The result is that on--demand work can articulate and track far more carefully than piecework historically could.

\topic{A second shift is  
%A number of factors in crowd work are different from piecework, chief among them being 
the relative ease with which the metaphorical ``assembly line'' can be changed.}
% Computers make it possible to switch from one task to another unlike any arbitrary manufacturing factory possibly could;
%modern on--demand workers on AMT and other platforms can more readily do any number of
%different \textit{types} of tasks in the span of just a few minutes
Historical manufacturing equipment was not Turing-complete, and could not quickly be assembled, edited, and redeployed.\msb{cite for historical piecework equipment being a large time + money investment?}
In contrast, today system--designers can share, modify, and instantiate environments
like sites of labor in a few lines of code
\cite{lessig2006code,turkitLittle}.
This opportunity has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to manipulate as few as 20 years ago
\cite{dai2015and,Cai:2016:CRI:2858036.2858237,cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

Third, modern crowd work has sliced work to such small scales that the marginal activities
--- things like finding work and cognitive task switching ---
have become relatively large compared to the tasks themselves
\cite{taskSearch}.
In the historical case of piecework,
moving metallurgical tools, mining equipment, or
other industry materials would have been prohibitively difficult and slow;
workers were encouraged to specialize in a single set of tasks,
allowing pieceworkers to sequence their tasks optimally on their own
\cite{hart2013rise}.
The result is that crowd workers are more free agents than historically was the case.
However, because they spend significant time searching for tasks, the piece rate is less a good estimate of take-home earnings than before.

% Rather than fall into the trap that \citeauthor{irani2015cultural} warns of,
% --- one which where crowd workers are rendered as
% ``modular, protocol--defined computational services'' ---
% we may yield better results from crowd work if we think of workers as similar to
% specialized, repurposable tools
% \cite{irani2015cultural}.
% \ali{feeling meh about this argument\dots}

\subsubsection{\implication}
If measurement precision limited the depth of decomposition for piecework historically, as \citeauthor{10.2307/23702539} argues, then modern on--demand work stands to become far more finely-sliced and highly decomposed than ever before.
Online tools make measurement and validation so easy~\cite{rzeszotarski2011instrumenting} that these aspects of piecework are solved, or near enough that they no longer limit task decomposition.
Now, not just tasks, but entire workers' histories~\cite{hata2017glimpse}, can be collected and analyzed in detail.
% crowd work research today is on the right track to investigate pipelining and meta--task design.
% That is, investigating better work discovery methods, producing tools for workers to make more informed decisions
% \cite[see, for example,][]{turkopticon}.

However, decomposition has hit a second bottleneck: cognition. 
Task switching costs and other cognitive costs make it difficult to work tasks so far decontextualized from their original intention \cite{delayAndOrderLasecki}.
There will of course be tasks that can be decomposed without much context, and these will form the most fine-grained of microtasks.
However, other tasks cannot be freed from context --- for example, logo design requires a deep understanding of the client and their goals.
In part due to this limitation, 99designs workers often recycle old designs rather than make new ones for each client~\cite{araujo201399designs}.

So, ultimately, the levels of decomposition are likely to follow the contours of context required. Low-context work will be extremely highly decomposed. High-context work will continue to be limited.
